Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families

### 2020-01-09 manuscript/accpeted_manuscript.tex
creating submitted and accepted versions for proper legal archiving

\documentclass[12pt]{article}  
\usepackage{amsmath}
\usepackage{url}
\usepackage[dvips]{graphicx}
\usepackage{multirow}
\usepackage{geometry}
\usepackage{pdflscape}
\usepackage{gensymb}
% \usepackage{rotating}
% make Figure 1 etc bold
\usepackage[labelfont=bf]{caption}
\usepackage{setspace}
\usepackage{multicol}

@@

@@

% \clearpage
\vspace{-0.25in}
\small{
\noindent\textbf{ORCID IDs}\\
\noindent Alyssa Cirtwill: https://orcid.org/0000-0002-1772-3868\\
\noindent Giulio V. Dalla Riva: https://orcid.org/0000-0002-3454-0633\\
\noindent Joshua A. Thia: https://orcid.org/0000-0001-9084-0959\\
\noindent Daniel B. Stouffer: https://orcid.org/0000-0001-9436-9674\\

\medskip
\noindent\textbf{Social media}: 
@acirtwill; @stoufferlab\\
\medskip
\noindent\textbf{Header}: 
Phylogenetic distance \& niche overlap
}

\noindent\small\textbf{Word Counts}
\begin{multicols}{2}
\small{
Main text: 6409 % Limit 6,500 % 
\vspace{-5pt}
\begin{itemize}
  \setlength\itemsep{-0.1em}
  \item Introduction: 1163
  \item Materials and Methods: 2469
  \item Results: 949
  \item Discussion: 1745
  \item Acknowledgements: 83
\end{itemize}
\bigskip
\bigskip
\bigskip

\noindent Figures: 3\\
\noindent Tables: 2\\
\noindent Notes: 1 file, 6 sections.}
\end{multicols}

@@

\end{spacing}
\begin{spacing}{1.5}
\clearpage

\section*{Introduction}
\linenumbers

>>>>

\documentclass[12pt]{article}  
\usepackage{amsmath}
\usepackage{url}
\usepackage[dvips]{graphicx}
\usepackage{multirow}
\usepackage{geometry}
\usepackage{pdflscape}
\usepackage{gensymb}
% \usepackage{rotating}
% make Figure 1 etc bold
\usepackage[labelfont=bf]{caption}
\usepackage{setspace}
\usepackage{multicol}
\usepackage{fancyhdr}

@@

\lhead{Accepted manuscript}

@@

\noindent This is the accepted version of the following article: \\
\smallskip
Cirtwill, A. R., Dalla Riva, G. V., Baker, N. J., Ohlsson, M.,
Norstr\"{o}m$^{4}$, I., Wohlfarth, I. M., Thia, J. A., Stouffer, D. B. (2020) \emph{Related plants tend to share pollinators and herbivores, but strength of phylogenetic signal varies among plant families}. \textbf{New Phytologist}: in press, which has been published in final form at \emph{link to paper}.\\
\smallskip
This article may be used for
non-commercial purposes in accordance with the Wiley Self-Archiving Policy [http://www.wileyauthors.com/self-archiving].

% % \clearpage
% \vspace{-0.25in}
% \small{
% \noindent\textbf{ORCID IDs}\\
% \noindent Alyssa Cirtwill: https://orcid.org/0000-0002-1772-3868\\
% \noindent Giulio V. Dalla Riva: https://orcid.org/0000-0002-3454-0633\\
% \noindent Joshua A. Thia: https://orcid.org/0000-0001-9084-0959\\
% \noindent Daniel B. Stouffer: https://orcid.org/0000-0001-9436-9674\\

% \medskip
% \noindent\textbf{Social media}: 
% @acirtwill; @stoufferlab\\
% \medskip
% \noindent\textbf{Header}: 
% Phylogenetic distance \& niche overlap
% }

% \noindent\small\textbf{Word Counts}
% \begin{multicols}{2}
% \small{
% Main text: 6409 % Limit 6,500 % 
% \vspace{-5pt}
% \begin{itemize}
%   \setlength\itemsep{-0.1em}
%   \item Introduction: 1163
%   \item Materials and Methods: 2469
%   \item Results: 949
%   \item Discussion: 1745
%   \item Acknowledgements: 83
% \end{itemize}
% \bigskip
% \bigskip
% \bigskip

% \noindent Figures: 3\\
% \noindent Tables: 2\\
% \noindent Notes: 1 file, 6 sections.}
% \end{multicols}

@@

% \end{spa cing}
% \begin{spacing}{1.5}
\clearpage

\section*{Introduction}
% \linenumbers
